The Revisited Hidden Weight Bit Function

### 2024-11-28 RevisedHiddenWeight.tex
minor+answer comments

\begin{align*}
\wtk{f}{k}(a)&=\sum_{x \in \Ekn{k}{n}} (-1)^{f(x)+ax}=\sum_{x \in \Ekn{k}{n}} (-1)^{\sum_{i=1}^{n/2} x_i x_{i+\frac{n}{2}}+ x_k +a \cdot x + \sum_{i=1}^{n/2} x_{n/2+i}}\\
&= \sum_{\pi(x) \in \Ekn{k}{n}} (-1)^{f(\pi(x))+a \cdot \pi(x)} =\sum_{\pi(x) \in \Ekn{k}{n}} (-1)^{\sum_{i=1}^{n/2} x_{\pi(i)} x_{\pi(i+\frac{n}{2})}+ x_{\pi(k)}+a \cdot \pi(x) + \sum_{i=1}^{n/2} x_{\pi(n/2+i)}}
\end{align*}
where $\pi$ is a permutation of $[1,n]$. 
We consider the permutation $\pi$ mapping the first half of $[1,n]$ to the odd positions and the second half to the even positions:
\[\pi(i)= \left\{ 
\begin{array}{l l}
2i-1 & \quad \text{ if } i\in [1,\frac{n}{2}], \\
2(i-\frac{n}{2}) & \quad \text{ if } i\in [\frac{n}{2}+1,n].
\end{array} \right. \] 
Regarding the restricted Walsh transform of $f$ it gives:
\begin{align*}
\wtk{f}{k}(a)&=\sum_{x\in \Ekn{k}{n}} (-1)^{\sum_{i=1}^{n/2} x_{2i-1} x_{2i}+ x_{\pi(k)} + \pi^{-1}(a) \cdot x + \sum_{i=1}^{n/2} x_{2i}}\\
&= \Dnka{n}{k}{d},
\end{align*}
where $d= \pi^{-1}(a) + e_{\pi(k)} +\sum_{i=1}^{n/2} e_{2i}$.

@@

@@

\begin{proof}
    It is enough to use the expressions from Table \ref{tab:Dnka_small_k}, and replace $p$, $q$ and $r$ by their respective values. For instance, for the case $n=16m$, we replace $p$, $q$ and $r$ by $m+s(s-1)$, $m+s(s+1)$ and $6m-2s^2$ in the expression $\Dnka n2a=2(p-q)^2-3(p+q)+r$, which yields $\Dnka n2a=0$. This checking can be autotomized by a computer algebra system. For this, we refer to the corresponding \textsf{SageMath} implementation from \cite{githubseure24}.\tsnote{@Pierrick, OK like this?}
\end{proof}

@@

>>>>

\begin{align*}
\wtk{f}{k}(a)&=\sum_{x \in \Ekn{k}{n}} (-1)^{f(x)+ax}=\sum_{x \in \Ekn{k}{n}} (-1)^{\sum_{i=1}^{n/2} x_i x_{i+\frac{n}{2}}+ x_k +a \cdot x + \sum_{i=1}^{n/2} x_{n/2+i}}\\
&= \sum_{\pi(x) \in \Ekn{k}{n}} (-1)^{f(\pi(x))+a \cdot \pi(x)} =\sum_{\pi(x) \in \Ekn{k}{n}} (-1)^{\sum_{i=1}^{n/2} x_{\pi(i)} x_{\pi(i+\frac{n}{2})}+ x_{\pi(k)}+a \cdot \pi(x) + \sum_{i=1}^{n/2} x_{\pi(n/2+i)}}
\end{align*}
where $\pi$ can be any permutation over $[1,n]$. 
In particular, we consider the permutation $\pi$ mapping the first half of $[1,n]$ to the odd positions and the second half to the even positions:
\[\pi(i)= \left\{ 
\begin{array}{l l}
2i-1 & \quad \text{ if } i\in [1,\frac{n}{2}], \\
2(i-\frac{n}{2}) & \quad \text{ if } i\in [\frac{n}{2}+1,n].
\end{array} \right. \] 
Regarding the restricted Walsh transform of $f$ it gives:
\begin{align*}
\wtk{f}{k}(a)&=\sum_{x\in \Ekn{k}{n}} (-1)^{\sum_{i=1}^{n/2} x_{2i-1} x_{2i}+ x_{\pi(k)} + \pi^{-1}(a) \cdot x + \sum_{i=1}^{n/2} x_{2i}}\\
&= \Dnka{n}{k}{d},
\end{align*}
where $d= \pi^{-1}(a) + e_{\pi(k)} +\sum_{i=1}^{n/2} e_{2i}$.

@@

\pmnote{Under revision}

@@

\begin{proof}
    It is enough to use the expressions from Table \ref{tab:Dnka_small_k}, and replace $p$, $q$ and $r$ by their respective values. For instance, for the case $n=16m$, we replace $p$, $q$ and $r$ by $m+s(s-1)$, $m+s(s+1)$ and $6m-2s^2$ in the expression $\Dnka n2a=2(p-q)^2-3(p+q)+r$, which yields $\Dnka n2a=0$. This checking can be autotomized by a computer algebra system. For this, we refer to the corresponding \textsf{SageMath} implementation from \cite{githubseure24}.\tsnote{@Pierrick, OK like this?}

    \pmnote{I think it works for the eprint (use the "ifnum\anon=" to be sure we do not forget it in an anonymous submission.

    I do not know if this will create a reference in your google scholar later one. Personally I would prevent that by just giving the link in the text, to avoid to have a reference that will have only 1 citation.

    	)}

@@

\pmnote{ degree of $h$, denoted by $e$ here is always greater than the AI, whereas $\degg(g)=d$ is smaller. It is consistent}
